\documentclass[12pt]{article}
\usepackage[a4paper]{geometry}
\usepackage[myheadings]{fullpage}
\usepackage{amsmath,amssymb,amsthm, enumitem, hyperref, tabto} 
\usepackage{fancyhdr}
\usepackage{arxiv}
\usepackage{lastpage}
\usepackage{graphicx, wrapfig, subcaption, setspace}
\usepackage[font=small, labelfont=bf]{caption} \usepackage{blindtext}
 \usepackage{blindtext}
\usepackage{url, lipsum}
\usepackage{tgbonum}
\usepackage{amsmath,physics}
\usepackage{authblk}
\usepackage{hyperref}
 \hypersetup{ 
     colorlinks=true, 
     linkcolor=blue, 
     filecolor=blue, 
     citecolor =red,
     urlcolor=cyan,
     pdftitle={emojis}
     } 
\usepackage[super,compress,sort,numbers]{natbib}
\usepackage{csquotes}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{algorithm}
\floatname{algorithm}{Algorithm}
\usepackage{times}
\usepackage{adjustbox}
\usepackage[T1]{fontenc}
\usepackage{makecell}
\usepackage{parskip}
\usepackage{erewhon}
\usepackage{geometry}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{framed}
\setlength\FrameSep{0.5em}
\setlength\OuterFrameSep{\partopsep}
\graphicspath{ {./images/} }
\usepackage{sectsty}

\sectionfont{\fontsize{15}{20}\selectfont}
\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} 
\usepackage[sorting=none]{biblatex}
\addbibresource{references.bib}

\newcommand{\HRule}[1]{\rule{\linewidth}{#1}}
\onehalfspacing
\setcounter{tocdepth}{5}
\setcounter{secnumdepth}{5}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\begin{document}


\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\footnotesize \emph{The Impact of Emoticons in Education}}
\fancyhead[R]{\footnotesize \emph{M22504}}
\fancyfoot[R]{Page \thepage\ of \pageref{LastPage}}


{\selectfont
\title{
	\huge \textbf{The Impact of Emoticons in Education}
}

\date{}

\author[1]{Lim Sue Han Justin}
\author[1]{Prannaya Gupta}
\affil[1]{NUS High School of Math and Science}

\maketitle



\begin{abstract}
\emph{The use of emojis has been of rising interest in the classroom setting. Specifically, with the rise of casual communication through text between teacher and student, the perceived value that emojis bring to the table is far more relevant. In this review, we collate and address the findings of recent literature on the topic of the pedagogical implications of emoticons.} \\
\begin{flushright}(215 words)\end{flushright}
\end{abstract}

\thispagestyle{empty}

\thispagestyle{empty}
\newpage

\section{Introduction}
...



For instance, given this passage, taken from Leemen Chan et al:

\begin{displayquote}
\emph{Although the history of human invention spans over millennia, there have been relatively few game-changing technologies. From the manipulation of fire back in the primal age to the invention of the electronic transistor in the 1940s, these monumental developments have often been followed up by fervent exploration and a burgeoning of new technologies that stem from that initial spark.}
\end{displayquote}



\begin{displayquote}
\emph{While some may say Artificial Intelligence, or AI, is akin to these other inventions, I beg to disagree.}
\end{displayquote}


A sample of the essay (partial) is shown below:
\begin{displayquote}
\textit{Asking multiple people for advice can very heavily influence how you may act on certain topics. Receiving advice from multiple people is not such a bad thing as it may seem. Receiving advice from multiple people is good because it can influence your decision, teach you more about the topic, and more points of view on the topic.}

\textit{Getting more peoples' opinions can heavily impact your decision. Having more opinions means more choices you can choose. This means that the more options you have, the easier it is to do the right thing. Others' opinions can stop you from doing the wrong thing. When they tell you their end it may impact you and stop you from doing something you wouldn't have wanted to do. Others' opinions can also show you what consequences there might be for your actions. They might tell you the possibilities of what might happen when you say that. People opinions can greatly impact what you do.}

\end{displayquote}



\section{References}

\printbibliography[
heading=none
]
}

\end{document}